\begin{abstract}
% Pitch (1-2 sentences): the problem and why it matters.
Test-time search --- self-consistency, best-of-$N$, beam search, and Monte Carlo
Tree Search (MCTS) --- is increasingly applied to make large language models (LLMs)
reason more reliably. Yet reported gains often compare a search method running
many model calls against a single greedy call, conflating the value of \emph{search}
with the value of \emph{extra compute}.
%
% Gap (1 sentence): what's missing.
It remains unclear not only \emph{when} structured search helps an LLM, but
\emph{what it should search over}.
%
% Contribution (2-3 sentences): what we do.
We present a controlled, \textbf{compute-matched} study of test-time search for
hierarchical vulnerability classification over the Common Weakness Enumeration
(CWE) taxonomy. Holding the policy LLM, prompt, and token budget fixed, we compare
search strategies and isolate three axes the literature entangles: \emph{policy
strength}, \emph{reward fidelity} (self-evaluation vs.\ a stronger external judge),
and---most consequentially---the \emph{search space}, contrasting MCTS over the
output taxonomy against MCTS over a free-form reasoning trajectory.
%
% Results: the numbers.
Three findings on a code-vulnerability benchmark (BigVul, patch-diff inputs).
(i) \emph{What you search over dominates}: MCTS over a reasoning trajectory beats
MCTS over the taxonomy by $+12$ leaf-accuracy points at \emph{half} the token
budget ($p{<}10^{-4}$), because taxonomy search commits to a wrong coarse
category on $60\%$ of examples and cannot recover, whereas reasoning search
defers commitment; moreover its accuracy is flat in the iteration knob, so the
gain comes from the reasoning \emph{scaffold} rather than the search machinery.
(ii) Search compensates \emph{weak} policies (up to $+8$ points over greedy) but
not strong ones, and its gain shrinks monotonically with policy strength;
self-consistency (sampling without a reward) captures almost none of it.
(iii) A stronger external judge leaves taxonomy search unchanged and does not
survive budget matching on reasoning search---the bottleneck is the policy and
the search space, not reward fidelity.
%
% Impact (1 sentence): why this matters beyond the paper.
We conclude that the design of the \emph{search space}, not the search budget or
the reward, is the primary lever for test-time search on structured outputs.
\end{abstract}
